Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2017-01-19 document/submission/ms.tex
Small corrections and addition to the affiliations, per request by coauthors.

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin R. Covey,\altaffilmark{5} J.F. Donati,\altaffilmark{6,7} Silvia H. P. Alencar,\altaffilmark{8} Gaitee A.J. Hussain,\altaffilmark{9,10} Benjamin J. Shappee,\altaffilmark{11,12} Gregory N. Mace,\altaffilmark{13} Jae-Joon Lee,\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}

\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Peking University, Yi He Yuan Lu 5, Haidian Qu, 100871 Beijing, People's Republic of China}
\altaffiltext{2}{KIPAC, Physics and Astronomy, Stanford University, Stanford, CA}
\altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
\altaffiltext{4}{Crimean Astrophysical Observatory, Nauchny, Crimea 298409, Russia}
\altaffiltext{5}{Department of Physics \& Astronomy, Western Washington University, Bellingham WA 98225-9164, USA}
\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F- 31400 France}
\altaffiltext{7}{Université de Toulouse, UPS-OMP, IRAP, 14 avenue E. Belin, Toulouse, F–31400 France}
\altaffiltext{8}{Departamento de F\`{\i}sica -- ICEx -- UFMG, Av. Ant\^onio Carlos, 6627, 30270-901 Belo Horizonte, MG, Brazil}
\altaffiltext{9}{European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching bei M\"unchen, Germany}
\altaffiltext{10}{Institut de Recherche en Astrophysique et Plan\'etologie, Universit\'e de Toulouse, UPS-OMP, F-31400 Toulouse, France}
\altaffiltext{11}{Carnegie Observatories, 813 Santa Barbara Street,
  Pasadena, CA 91101, USA}
\altaffiltext{12}{Hubble, Carnegie-Princeton Fellow}
\altaffiltext{13}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
\altaffiltext{14}{Korea Astronomy and Space Science Institute, 776 Daedeok-daero, Yuseong-gu, Daejeon 305-348, Korea.}
\altaffiltext{15}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
\altaffiltext{16}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
\altaffiltext{17}{Institute of Astronomy and Astrophysics, Academia Sinica
(ASIAA), P.O. Box 23-141, Taipei 10641, Taiwan}

>>>>

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3,18} Konstantin Grankin,\altaffilmark{4} Kevin R. Covey,\altaffilmark{5} J.F. Donati,\altaffilmark{6,7} Silvia H. P. Alencar,\altaffilmark{8} Gaitee A.J. Hussain,\altaffilmark{9,10} Benjamin J. Shappee,\altaffilmark{11,12} Gregory N. Mace,\altaffilmark{13} Jae-Joon Lee,\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}

\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Peking University, Yi He Yuan Lu 5, Haidian Qu, 100871 Beijing, People's Republic of China}
\altaffiltext{2}{KIPAC, Physics and Astronomy, Stanford University, Stanford, CA}
\altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
\altaffiltext{4}{Crimean Astrophysical Observatory, Nauchny, Crimea 298409, Russia}
\altaffiltext{5}{Department of Physics \& Astronomy, Western Washington University, Bellingham WA 98225-9164, USA}
\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F- 31400 France}
\altaffiltext{7}{Université de Toulouse, UPS-OMP, IRAP, 14 avenue E. Belin, Toulouse, F–31400 France}
\altaffiltext{8}{Departamento de F\`{\i}sica -- ICEx -- UFMG, Av. Ant\^onio Carlos, 6627, 30270-901 Belo Horizonte, MG, Brazil}
\altaffiltext{9}{European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching bei M\"unchen, Germany}
\altaffiltext{10}{Institut de Recherche en Astrophysique et Plan\'etologie, Universit\'e de Toulouse, UPS-OMP, F-31400 Toulouse, France}
\altaffiltext{11}{Carnegie Observatories, 813 Santa Barbara Street,
  Pasadena, CA 91101, USA}
\altaffiltext{12}{Hubble, Carnegie-Princeton Fellow}
\altaffiltext{13}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
\altaffiltext{14}{Korea Astronomy and Space Science Institute, 776 Daedeok-daero, Yuseong-gu, Daejeon 305-348, Korea.}
\altaffiltext{15}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
\altaffiltext{16}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
\altaffiltext{17}{Institute of Astronomy and Astrophysics, Academia Sinica (ASIAA), Taipei 10617, Taiwan}
\altaffiltext{18}{VIDA Postdoctoral Fellow}
